---
format: gfm
execute: 
  echo: false
---

<!-- README.md is generated from README.qmd. Please edit that file -->

```{r}
#| label: setup
targets::tar_config_set(
  store = here::here("_targets"),
  script = here::here("_targets.R")
)
```

# Quarto Research Blog

## Research Wokflow

This is an example of a research workflow using [Quarto](https://quarto.org) and [`targets`](https://books.ropensci.org/targets/).

### Explanation

- [Zenn](https://zenn.dev/nicetak/articles/workflow-research-2025) (in Japanese)

### Replication

1. Install R, Julia, and Quarto
1. Set Julia path in .Renviron `PATH_JULIA="/path/to/julia"`
1. Install `renv` in R console
1. Run `renv::restore()` to install packages
1. Run `targets::tar_make()` to run the workflow

```{r}
#| label: mermaid-workflow
#| output: asis
cat("``` mermaid\n")
cat(
  targets::tar_mermaid(
    targets_only = TRUE,
    outdated = FALSE,
    legend = FALSE,
    color = FALSE,
  ),
  sep = "\n"
)
cat("\n```")
```


## Quarto Research Blog

This is also an example of a research blog using the [Quarto](https://quarto.org).
You can find a [website](https://kazuyanagimoto.com/quarto-research-blog/) and
a password-protected [website](https://kazuyanagimoto.com/quarto-research-blog/).

- username: `abcd`
- password: `1234`

### Explanation

- [My blog](https://kazuyanagimoto.com/blog/2024/04/05/)
- [Zenn](https://zenn.dev/nicetak/articles/quarto-research-blog) (in Japanese)

