# Model {#sec-model}

```{r}
#| label: setup-model
#| include: false
library(dplyr)
library(ggplot2)
library(tinytable)

targets::tar_config_set(
  store = here::here("_targets"),
  script = here::here("_targets.R")
)

targets::tar_load(c(parameters))
invisible(list2env(targets::tar_read(fns_graphics), .GlobalEnv))

theme_set(theme_proj())
options(tinytable_html_mathjax = TRUE)
```

@aiyagari1994 introduced a model of the economy with heterogenous agents and incomplete markets. The model is a discrete-time, infinite-horizon model with stochastic labor productivity.

## Model Setup

The model is a discrete-time, infinite-horizon model with stochastic labor productivity. The economy consists of a continuum of agents with different levels of capital and labor productivity. Each agent chooses how much capital to accumulate in order to maximize their lifetime utility.

The utility function is given by:

$$
u(c) = \frac{c^{1-\gamma} - 1}{1-\gamma}.
$$

The production function is defined as a Cobb-Douglas function:

$$
F(K, L) = K^\alpha L^{1-\alpha}.
$$

The log labor productivity $l_t$ follows an AR(1) process:

$$
l_t = \rho l_{t-1} + \epsilon_t, \quad \epsilon_t \sim N(0, \sigma^2).
$$

ABBREVIATED


## Calibration

Standard values in the literature are used for the calibration. @tbl-parameters shows the parameters used in the model.

```{r}
#| label: tbl-parameters
#| tbl-cap: Model Parameters
tibble(
  Parameter = c(
    "$\\gamma$",
    "$\\beta$",
    "$\\delta$",
    "$\\alpha$",
    "$b$",
    "$\\rho$",
    "$\\sigma$"
  ),
  Value = c(
    parameters$gamma,
    parameters$beta,
    parameters$delta,
    parameters$alpha,
    parameters$b,
    parameters$rho,
    parameters$sigma
  ),
  Description = c(
    "Coefficient of relative risk aversion",
    "Discount factor",
    "Depreciation rate",
    "Capital share in output",
    "Upper bound of debt",
    "Persistence of labor productivity",
    "Standard deviation of labor productivity shock"
  )
) |>
  tt()
```